Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-12 analysis/paper/paper.Rmd
Add model methods

The models' were structured as follows to predict two responses, computational methods and data availability.
For the the publishing journal (abbreviation was used throughout) (formula: response ~ abbreviation) and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
The effects of year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).

>>>>

The models' were structured as follows to predict two responses, computational methods and data availability.
To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee and year as random effects (formula: list(~1 | assignee, ~1 | year)).
To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
To predict the responses with the journals' open access policies the formula took the form response ~ open and included abbreviation, assignee and year as random effects (formula: list(~1 | abbreviation, ~1 | assignee, ~1 | year)).
